---
title: "Linear Regression to Feed Forward Network"
author: "Theresa Alexander"
date: "1/23/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#load packages
```{r}
#caret for easy machine learning workflow
library(caret)
#MASS, for computing stepwise regression
library(MASS)
```


#load data
```{r}
college = read.csv("~/Downloads/College.csv", row.names =  1, header = TRUE)

college$preference = college$Accept/college$Apps
#look at first few rows of the data
head(college)
```

We see we have 777 colleges that we've collected data for. We have 18 variables, or "features", we can use in our models. 


#Linear Regression

Remember what the relationship between room board and graduation rate?
```{r}
plot(x = college$preference, y = college$Grad.Rate, pch = 19, col = "blue", xlab = "Preference", ylab = "Graduation Rate", main = "Linear Relationship")
```


We see a decent linear relationship here, so let's make a simple linear regression model with the x variable Room.Board and the y variable Grad.Rate to see exactly how much Room Board changes Graduation Rate.

##Research Question 1

How much does Room Board effect the change in Graduation Rate?

Graduation Rate = m * Room Board + b

##Simple Linear Regression
```{r}
#create the linear model using the lm() function
linear_model = lm(Grad.Rate ~ Room.Board, data = college)

#print the summary of results from the simple linear regression lm() made
summary(linear_model)

```

The lm() function has estimated the the equation to be 

Graduation Rate = 36.46 + .006656 * Room Board, 

which means that the Room Board is $0, the graduation rate is 36.46%. Then, with every dollar increase for the Room Board, the Graduation Rate increases by .007%. 
